Stage-Splitting a Modal Language

### 2014-06-28 paper/splitting.tex
Bunch of changes to figures.
changed defn of hold
worked on intro to splitting. need to merge with uncommitted stuff at home

Motivate splitting here.  (Depends on intro)
Consider splitting at \bbtwo. 
The basic idea is that, for a given input program, we want to find all of the stage \bbone\ content, pull that out into a single term, 
and also produce a stage \bbtwo\ term, which takes the results of the stage \bbone\ part and produces the final answer.
We call these two parts the {\em precomputation} and the {\em residual}, respectively.
More formally, we want to take some $\coltwo e A$ and produce a $p : \tau$ and a $r : \tau \to A$ such that $e$ and $(r~p)$ reduce to the same value.

@@

\begin{lstlisting} 
prev{
  let x = (next {1+2}, 3+4) in
  next{prev{#1 x} * prev{#1 x} * prev{hold(#2 x)}}
}
\end{lstlisting}

@@

\input{figures/splitting-term}
\input{figures/splitting-sumfun}

>>>>

The basic idea is that we want to take a term which contains interleaved stage \bbone\ and stage \bbtwo\ code
and untangle it into two separate terms: one with all of the stage \bbone\ code and one with all the stage \bbtwo\ code.
To facilitate communication between the stages, there is a data structure passed between the stages, 
which is an output of the stage \bbone\ term and and input to the stage \bbtwo\ term.

As with the dynamics, the form of the splitting statement depends on the external stage of the term.
We consider splitting for stage \bbtwo\ terms first, as it has a simpler form.  
For example, take \verb|hold{1+2} < 5|.
We can split this into two separate terms, \verb|1+2| and \verb|fn l => l < 5|, 
which are called the {\em precomputation} and {\em residual}, respectively.  
For this splitting to be correct, the residual applied to the precomputation should yield the same result as the original term.

The form of splitting for stage \bbone\ terms is more complicated.

@@

\begin{lstlisting} 
prev{
  let x = (next {1+2}, 3+4) in
  next{prev{#1 x} * prev{#1 x} * hold{#2 x}}
}
\end{lstlisting}

@@

\input{figures/splitting-term}
